Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-09-20 SDSS Journal Paper/Paper Draft.Rmd
Fixing point #8 (no more specificity but at least avoiding the "small subset" language)

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. We select a small subset of towns (out of the 999 towns in Iowa) and a small subset of variables of interest to start with, and then allow the user to increase the complexity of the display in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload [@few].

>>>>

The large set of publicly available data (primarily from \url{data.iowa.gov}) we have assembled is useful, but we must be careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. \svp{The user selects a single town of interest and we add summary variables reflecting QoL metrics such as distance to local schools and city budget. Then, the user can} in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload [@few].
